The letter

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
Minor change to Future Work section

In addition, we have assumed that the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic. However, the assumption of homogeneity is quite strong. Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed. Future work should also include a more realistic synaptic response kernel, with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.

>>>>

In addition, we have assumed that the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic. However, the assumption of homogeneity is quite strong. Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed. Future work should also include a synaptic response kernel with finite rise and decay times, and finite distant dependant propagation times into the parametric neural field equations.
